Mapping

### 2025-04-04 episodes/phylogenetics.Rmd
Change to current uppmax project

 ```bash
interactive -A uppmax2024-2-10 -M snowy -t 4:00:00
module load bioinfo-tools iqtree
cd /proj/g2020004/nobackup/3MK013/<username>/phylogenetics
```

>>>>

 ```bash
interactive -A uppmax2025-3-4 -M snowy -t 4:00:00
module load bioinfo-tools iqtree
cd /proj/g2020004/nobackup/3MK013/<username>/phylogenetics
```

### 2025-04-04 episodes/snps-phylogeny.Rmd
Change to current uppmax project

```bash
interactive -A uppmax2024-2-10 -M snowy -t 04:00:00
cd /proj/g2020004/nobackup/3MK013/<username>/molepi/data
mv trimmed_fastq trimmed_fastq_partial
tar xvzf ../../../data/trimmed_fastq.tar.gz
ls trimmed_fastq
```

@@

```bash
interactive -A uppmax2024-2-10 -M snowy -t 04:00:00
cd /proj/g2020004/nobackup/3MK013/<username>/molepi/data
mkdir snps
```

@@

```bash
module load snippy
```

Snippy is fast but a single run still takes about 2-3 minutes. We would therefore tell snippy to run all the samples after each other. However this time we cannot use a wildcard to do so. We would instead run all the samples in a loop. The "real" loop is commented out, and we use one that runs only the sample we've analyzed so far.

@@

```bash
head -n10 ~/molepi/results/snps/ERR029206/snps.tab 
```

@@

```bash
cd /proj/g2020004/nobackup/3MK013/<username>/molepi/results
mv snps snps_partial
mkdir snps
cd snps
tar xvzf ../../../../data/snps.tar.gz
ls
```

```output
ERR026473     ERR026482
ERR026474     ERR029206
ERR026478     ERR029207
ERR026481
```

@@

```bash
ls ERR026473
```

```output
ref.fa          snps.filt.vcf   snps.tab
ref.fa.fai      snps.gff        snps.txt
snps.aligned.fa snps.html       snps.vcf
snps.bam.bai    snps.log        snps.vcf.gz
snps.bed        snps.raw.vcf    snps.vcf.gz.csi
snps.csv        snps.subs.vcf
```

@@

```bash
cat ~/molepi/results/snps/ERR029207/snps.txt
```

@@

```bash
cd /proj/g2020004/nobackup/3MK013/<username>/molepi/results
snippy-core --ref=../../data/GCF_000195955.2_ASM19595v2_genomic.fna ERR026473 ERR026474 ERR026478 ERR026481 ERR026482 ERR029206 ERR029207
```

>>>>

```bash
interactive -A uppmax2025-3-4 -M snowy -t 04:00:00
cd /proj/g2020004/nobackup/3MK013/<username>/molepi/data
mv trimmed_fastq trimmed_fastq_partial
tar xvzf ../../../data/trimmed_fastq.tar.gz
ls trimmed_fastq
```

@@

```bash
interactive -A uppmax2025-3-4 -M snowy -t 04:00:00
cd /proj/g2020004/nobackup/3MK013/<username>/molepi/data
mkdir snps
```

@@

```bash
module load bioinfo-tools snippy
```

Snippy is fast but a single run still takes about 15 minutes. We would therefore tell snippy to run all the samples after each other. However this time we cannot use a wildcard to do so. We would instead run all the samples in a loop. The "real" loop is commented out, and we use one that runs only the sample we've analyzed so far.

@@

```bash
head -n10 ../../results/snps/ERR029206/snps.tab 
```

@@

```bash
cd /proj/g2020004/nobackup/3MK013/<username>/molepi/results
mv snps snps_partial
mkdir snps
cd snps
tar xvzf ../../../../data/snps.tar.gz
ls *
```

```output
ERR026473:
ref.fa.          snps.bam.bai  snps.filt.vcf  snps.log	     snps.tab  snps.vcf.gz
ref.fa.fai	     snps.bed      snps.gff       snps.raw.vcf   snps.txt  snps.vcf.gz.csi
snps.aligned.fa  snps.csv      snps.html      snps.subs.vcf  snps.vcf

ERR026474:
ref.fa		       snps.bam.bai  snps.filt.vcf  snps.log	     snps.tab  snps.vcf.gz
ref.fa.fai	     snps.bed      snps.gff       snps.raw.vcf   snps.txt  snps.vcf.gz.csi
snps.aligned.fa  snps.csv      snps.html      snps.subs.vcf  snps.vcf
```

@@

@@

```bash
cat /proj/g2020004/nobackup/3MK013/<username>/molepi/results/snps/ERR029207/snps.txt
```

@@

```bash
cd /proj/g2020004/nobackup/3MK013/<username>/molepi/results/snps
snippy-core --ref=../../data/GCF_000195955.2_ASM19595v2_genomic.fna ERR026473 ERR026474 ERR026478 ERR026481 ERR026482 ERR029206 ERR029207
```
